### 2019-01-03 index.Rmd
Pushing 0.0-6

>>>>

```{r, echo = FALSE, fig = TRUE, results = 'hide', fig.width = 12, fig.height = 6.5}
col <- rev(colorspace::sequential_hcl(21, h = c(-50, 120), c. = c(80, 10)))
image(mod, FUN = "freq", deltad = 7L,
      col = col, contours = TRUE, drawlabels = FALSE,
      main = "Hourly foehn Frequency Diagram, Weekly Aggregation")
```
